---
title: "Data Exploration"
execute: 
  echo: false
  message: false
  warning: false
---

The data were obtained from IPEDS. We include 4 year public or not-for-profit private institutions in the United States that are degree-granting, primarily baccalaureate or above with between 1,000-9,999 students.

```{r}
#| label: read-data
library(tidyverse)
dat <- read_csv("data/final_data.csv")
```

<!-- Describe the data below here. How many observations are there? How many variables? What are the observations? -->

Our variable of interest is _______, measured in the 2018-2019 cohort. Our outcome of interest is first-year retention rate, measured in 2019-2020 (i.e. what proportion of the first year cohort that began in 2018-2019 returned in Fall 2019). Below is a plot visualizing the relationship between these variables, before adjusting for potential confounders.

```{r}
#| label: figure-1

## Insert your plot code here.
```

<!-- Describe what you see in the plot here. -->

Below is a table of the collected variables.

<!-- Move your variable of interest to the top of the list below. -->

```{r}
#| label: table-one

library(gtsummary)

tbl_summary(dat, include = c(
  "retention_rate",    
  "degree_status",
  "institution_cat",
  "size_cat",
  "n_firstyear_enrolled",
  "carneigie_cat",
  "religious_affiliation",
  "total_price_local",
  "total_price_instate",
  "total_price_outofstate",
  "disabilities_percent",
  "total_enrollment",
  "percent_asian",
  "percent_black_or_african_american",
  "percent_hispanic",
  "percent_white",
  "percent_women",
  "percent_all_distance",
  "percent_some_distance",
  "student_faculty_ratio",
  "average_instructor_salary",
  "percent_finanical_aid",
  "percent_pell_grant",
  "graduation_rate",
  "require_test_score",
  "total_applicants",
  "total_men_applicants",
  "total_men_applicants",             
  "total_women_applicants",           
  "total_admitted",                   
  "total_men_admitted",               
  "total_women_admitted",             
  "total_enrolled",                   
  "total_men_enrolled",               
  "total_women_enrolled",             
  "percent_admitted",                 
  "student_service_expenses",         
  "endowment_assets",                 
  "major_education",                  
  "major_engineering",                
  "major_biological_sciences",        
  "major_mathematics",                
  "major_physical_sciences",          
  "major_business"                  
))
```

