---
title: "Sensitivity Analyses"
execute: 
  echo: false
  message: false
  warning: false
---


## Athletics Data

```{r}
library(tidyverse)
athletics_dat <- read_csv("data/basketball_data_2018.csv")
```

Our original dataset did not have data on athletics rankings. As a sensitivity analysis, we have obtained data that includes the "Power Rating" (chance of beating an average Division I team) in 2018 for a subset of schools. Below are the results of our model, adding in this variable.

<!-- Fill in the sentence below with the number of observations in the athletics_dat dataset. -->

This data set includes information on XX schools.

<!-- Add in your model in the ... and set `eval: true` -->

```{r}
#| eval: false
lm(retention_rate ~ ... + bball_power_rating, data = athletics_dat)
```

<!-- Add an explanation of what you see. Does adding this variable change your findings from your final model? -->

## USNews Ranking Data

```{r}
usnews_dat <- read_csv("data/usnews_data_2018.csv")
```

Our original dataset did not have data on USNews rankings. As a sensitivity analysis, we have obtained rankings from 2018. Below are the results of our model, adding in this variable.

<!-- Fill in the sentence below with the number of observations in the usnews_dat dataset. -->

This data set includes information on XX schools.

<!-- Add in your model in the ... and set `eval: true` -->

```{r}
#| eval: false
lm(retention_rate ~ ... + usnews_ranking, data = usnews_dat)
```

<!-- Add an explanation of what you see. Does adding this variable change your findings from your final model? -->


